---
title       : Developing Dataproducts Project
subtitle    : Shiny and Slidify 
author      : Willem Moors
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Read And Weep

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- .class #id 

## Greatest difference between 1990 and 2012 

For example the difference for all countries between 1990 and 2010 can be calculated as follows: 

```{r}
le<-readRDS("countrydata.rds")
ledif<-      merge( le[ le$year==1990, c("country","le_birth")],
                    le[ le$year==2012, c("country","le_birth")],
                    by="country")

ledif$df=ledif$le_birth.y-ledif$le_birth.x
head(ledif)
```

--- 
## Greatest negative change 

Countries with the greatest negative change between 1990 and 2010: 
```{r}
head( ledif[order(ledif$df),c(1,4)])
```


--- 
## Greatest positive change 

Countries with the greatest positive change between 1990 and 2010:
```{r}
head( ledif[order(-ledif$df),c(1,4)])
```


--- .class #id 

## Slide 2

Slide 2 is interesting


